---
title: "RYandexTranslate"
author: "Mukul Chaware"
date: "9 March 2016"
output: html_document
---

R Interface to Yandex Translate API. [Yandex Translate](https://translate.yandex.com/) is
a statistical machine translation system. The system translates separate words, complete 
texts, and webpages. This package can be used to detect language from text and to 
translate it to supported target language.

###Installation

To install from CRAN repository:

```{r eval=F}
install.packages("RYandexTranslate")
```

To install from github:

```{r eval=F}
library(devtools)
install_github("mukul13/RYandexTranslate")
```

To get free API key, sign up [here](https://tech.yandex.com/translate/doc/dg/concepts/api-overview-docpage/)

```{r eval=F}
api_key="YOUR API KEY"
```


###Examples

To list all functions supported by RYandexTranslate package

```{r eval=F}
library(RYandexTranslate)
ls("package:RYandexTranslate")
```

```{r eval=F}
#>"detect_language"   "get_translation_direction"   "translate"   
```

To get a list of translation directions supported by the service

```{r eval=F}
directions=get_translation_direction(api_key)
head(directions$dirs)
```

```{r eval=F}
#>"az-ru" "be-bg" "be-cs" "be-de" "be-en" "be-es"
```

To detect the language of the specified text

```{r eval=F}
data=detect_language(api_key,text="how are you?")
data
```

```{r eval=F}
#>"en"
```

To translate text to the specified language

```{r eval=F}
data=translate(api_key,text="how are you?",lang="en-hi")
data
```

```{r eval=F}
#>$lang
#>[1] "en-hi"
#>
#>$text
#>[1] "आप कैसे हैं?"
```

###Resources
* [Github repo](https://github.com/mukul13/RYandexTranslate)
* [Yandex Translate API](https://tech.yandex.com/translate/doc/dg/concepts/About-docpage)

